---
title: "Data Set Overview"
author: "~CB"
date: "`r format(Sys.time(), '%d. %B, %Y')`"
output:
  html_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## 1 Post data

* 18 million posts to Facebook from public schools in the US

### Potential post variables

```{r}
f <- 'json/2020-20.json'
d <- jsonlite::fromJSON(f, simplifyDataFrame = TRUE, flatten = TRUE)$result$posts
d %>% 
  janitor::clean_names() %>% 
  names()
d %>% 
  head(2) %>% 
  knitr::kable()
```

### Currently sampled post-level variables:

* post creation timestamp

* post url

* user_name / account identifier

* nces_id to join school and district data
  * whether school-level NCES data is available for post (ca. 5 out of 18 million)
  * whether district-level NCES data is available for post (ca. 13 out of 18 million)

* whether the post shares a **photo**

* whether the post shares a **video**

* whether the post shares a **link**

### In addition: Considering media types

```{r, cache=TRUE}

# d <- targets::tar_read(json)
# d %>% 
#   select(media, type) %>% 
#   unlist() %>% 
#   table() %>% 
#   sort() %>% 
#   rev() %>% 
#   saveRDS('var-overview_cache/media_overview.rds') # cache failed...

readRDS('var-overview_cache/media_overview.rds') %>% 
  knitr::kable()
  
# Example URLs
# d %>% 
#   filter(!duplicated(type)) %>% 
#   select(type, post_url) %>% 
#   arrange(type) %>% 
#   saveRDS('var-overview_cache/media_exampled.rds') 
  
readRDS('var-overview_cache/media_exampled.rds') %>% 
  knitr::kable()

```

## 2 NCES data

* NCES data on public schools and districts, matched through extracting profile identifiers from URLs scraped from school webpages

* N = 99,603 public schools
  * 5,634 of which have school pages in Facebook post data
    * many schools web pages seem to link to their district's Facebook page
    * *but these few school pages are still responsible for around 25% of posts, ~ 5 million!*

* N = 9,949 districts
  * 8,112(!) of which are represented in Facebook post data, making up ~ 13 million out of 18 million posts
  
* Only 90,000 out of 18 million posts have neither NCES school nor NCES district data, but each page is linked
*either* to a NCES school *or* NCES district

### Potential variables

```{r}

d <- targets::tar_read(nces_all)

# Schools

d$schools %>% 
  names()

d$schools %>% 
  head(3) %>% 
  knitr::kable()

# Districts

d$districts %>% 
  names()

d$districts %>% 
  head(3) %>% 
  knitr::kable()

```

## 3 School and district level aggregates for descriptives and predictive modeling

### Currently selected variables, aggregated variables, and descriptives

```{r}

all_numbers <- function(v) 
  return(all(na.omit(str_detect(v, '[0-9\\.]'))))

d <- targets::tar_read(agg_school)

d %>% 
  names()

d %>% 
  head(3) %>% 
  knitr::kable()

d %>% 
  mutate_if(all_numbers, as.numeric) %>% 
  skimr::skim()

d <- targets::tar_read(agg_district)

d %>% 
  names()

d %>% 
  head(3) %>% 
  knitr::kable()

d %>% 
  mutate_if(all_numbers, as.numeric) %>% 
  skimr::skim()

```


## 4 Sampled data set including hand-coding

* number of faces and number of identifiable faces of students, staff, and teachers

* ... and many more!

```{r}

d <- targets::tar_read(sampled)

all_numbers <- function(v) 
  return(all(na.omit(str_detect(v, '[0-9\\.]'))))

d %>% 
  mutate_if(all_numbers, as.numeric) %>% 
  skimr::skim()

```

